Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-24 paper.tex
phrasing
Distinguish bibliography from references
Implement some recommended edits

@@

\subsection{Thesis/Argument}
Piracy should not be hastily thrown aside.
Piracy is an excellent tool for disseminating information, services, content,
\&c. that may not have been available any other way.

\section{Arguments For Piracy}
As mentioned above, even though piracy is illegal, there is still merit to the tools of
piracy and the values behind them. The merits of piracy can be divided into three realms:
equal access to information, governance, and privacy. 
\subsection{Equal Access}
At its core, piracy is primarily concerned with accessing information of all kinds,
regardless of whether someone is authorized to access that information or not. This is
what piracy is best at and, contrary to popular belief, it is not always a bad thing.

@@

\subsubsection{Response}
An argument that focuses solely on the criminality of the actions of piracy
may present a strong deterrent for many that would consider piracy. It is true
that the repercussions of piracy can be great, and it is true that in many
cases both parties may be liable for damages or in danger of prison sentences.
Christians should consider these things deeply. We are called to be meek,
merciful, and peaceful (Matthew 5:5, 7, 9; Galatians 5:22-26). We are also
called to harmony (Romans 12:16--18, Galatians 5:15-17). Christians have
pondered on the questions of civil disobedience. While we are called to peace,
love, and obedience, our obedience to man should not disrupt our obedience to
God. Clearly, the Bible does not call for anarchy (see Romans 13), but it
does present some cases in which civil disobedience for a greater good (that
aligns with God's values) supersedes extreme patriotism.~\footnote{%
  See the examples of the Hebrew midwives of Exodus 1; see also Rahab's defence
  of the Israelite spies; see also Daniel's disobedience to King
  Nebuchadnezzar; see also examples of civil disobedience in Revelation 13:15%
} Christians have some precedent for civil disobedience, but, at the same time,
Christians should also expect that there will be punishments for our actions.
While the legislation against piracy is not always evil (and thus does not
call for Christians to exert some civil disobedience), some of it can call our
consciences into question, especially when we consider critical research such
as the medical advances that have been discussed earlier in this paper.

@@

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed. 
The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by Mezzour et al. reveals that piracy is not equal
around the globe, and it poses serious problems especially for people in
poor countries where piracy is widespread. Although they hypothesized, like
other researchers, that \textcquote{mezzour:empirical-study}[,]{%
  cyber criminals would target rich countries because the monetary benefit of
  compromising rich people's computers is higher
} but they found that, \textcquote{mezzour:empirical-study}[.]{%
  surprisingly, poor countries in Sub-Saharan Africa because of the low cost of
  attacking computers in this region%
} Mezzour et al. conclude that, due to the high correlation between piracy
and malware, one of the policy implications is that Sub-Saharan Africa requires
reducing piracy to combat the spread of malware.
Antivirus provider Kaspersky recently uncovered an example of malware spreading
through pirated software.~\cite{pcmag:malware}

@@

There are few (if any) types of illegal content that rival that of child
pornography. It is a very sad reality, but this type of content is distributed
widely through the use of the Internet. Why and how this happens is perhaps out
of scope for this paper, but part of may be due to a sense of privacy and
anonymity that is fostered to an extreme in certain subcultures of the
Internet.~\cite[588]{prichard:subcultures} Research reveals that piracy and
piracy-adjacent tools provide the means to distribute this disgusting content
to unimaginable scales. Prichard et al explored this area of research, with
the following conclusions:
\blockcquote[593]{prichard:subcultures}{%
  Based on longitudinal data collected between August and November 2010, this
  study screened for the search terms that still appeared in the isoHunt Top
  300 list in November after being observed during August. In summary, the
  study found that 158/162 search terms related to infringing content, while
  3/162 search terms related to child pornography and 1/162 to bestiality%
}
The consistently widespread nature of this immoral and illegal content presents
a really compelling argument against piracy for Christians.

@@

This may be an unsatisfactory and complex answer to a large and complex issue.
Piracy (namely in the form of torrenting) does, however, rely on peers to
seed the content, and if changes can be made in these subcultures of the
internet via evangelizing, perhaps there is hope for a better piracy community.

@@

On the one hand, a Christian use of piracy should be respectful of authority.
We are called to do this regardless of punishment, but as a matter of
conscience (Romans 13:4--5). We are to exercise our freedom respectfully and
not as a cover-up for evil (1 Peter 2:13--7). In other words, we should consider
both the consequences we may incur and the image we portray carefully before
making a conclusion about the practice of piracy. A proper consideration of
privacy should not ignore the serious ramifications and associations that come
with it.

@@

\clearpage
\nocite{*}
\printbibliography
\end{document}

>>>>

\begin{refsection}

@@

\subsection{Thesis/Argument}
Piracy should not be hastily thrown aside nor should it be accepted
wholeheartedly in every situation. Piracy is an excellent tool for
disseminating information, services, content, \&c. that may not have been
available any other way. As a Christian, a proper exploration of piracy should
consider the potential benefits (or circumstances that warrant piracy) and the
potential downsides (or circumstances that need special attention from
Christian developers, writers, and netizens).

\section{Arguments For Piracy}
As mentioned above, even though piracy is illegal, there is still merit to the tools of
piracy and the values behind them. The merits of piracy can be divided into three realms:
equal access to information, governance, and privacy.

\subsection{Equal Access}
At its core, piracy is primarily concerned with accessing information of all kinds,
regardless of whether someone is authorized to access that information or not. This is
what piracy is best at and, contrary to popular belief, it is not always a bad thing.

@@

\subsubsection{Response}
An argument that focuses solely on the criminality of the actions of piracy
may present a strong deterrent for many that would consider piracy. It is true
that the repercussions of piracy can be great, and it is true that in many
cases both parties may be liable for damages or in danger of prison sentences.
Christians should consider these things deeply. We are called to be meek,
merciful, and peaceful (Matthew 5:5, 7, 9; Galatians 5:22-26). We are also
called to harmony (Romans 12:16--18, Galatians 5:15-17). Christians have
pondered on the questions of civil disobedience. While we are called to peace,
love, and obedience, our obedience to man should not disrupt our obedience to
God. Clearly, the Bible does not call for anarchy (see Romans 13), but it
does present some cases in which civil disobedience for a greater good (that
aligns with God's values) supersedes extreme patriotism.~\footnote{%
  See the examples of the Hebrew midwives of Exodus 1; see also Rahab's defence
  of the Israelite spies; see also Daniel's disobedience to King
  Nebuchadnezzar; see also examples of civil disobedience in Revelation 13:15%
} Christians have some precedent for civil disobedience, but, at the same time,
Christians should also expect that there will be punishments for our actions.

As the arguments against piracy that follow in this paper, one should consider
that legislation against piracy is not always evil; there are valid concerns
with piracy's immoral/illegal content and economic damages. Christians should
be careful to call upon civil disobedience as a defense for their piracy habits
online. On the other hand, we also need to consider some cases in which being
a seeder could benefit our neighbors with less resources to legally obtain
research, software, or files that could benefit the general population.

@@

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed. 
The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by Mezzour et al. reveals that piracy is not equal
around the globe, and it poses serious problems especially for people in
poor countries where piracy is widespread. Although they hypothesized, like
other researchers, that \enquote{cyber criminals would target rich countries}
because of monetary incentives, they found that, cyber criminals targeted
\textcquote{mezzour:empirical-study}[.]{%
  poor countries in Sub-Saharan Africa because of the low cost of attacking
  computers in this region%
} Mezzour et al. conclude that, due to the high correlation between piracy
and malware, one of the policy implications is that Sub-Saharan Africa requires
reducing piracy to combat the spread of malware.
In more recent news, Antivirus provider Kaspersky recently uncovered an example
of malware spreading through pirated software.~\cite{pcmag:malware}

@@

There are few (if any) types of illegal content that are as immoral as that of
child pornography. It is a very sad reality, but this type of content is
distributed widely through the use of the Internet. Why and how this happens is
perhaps out of scope for this paper, but part of may be due to a sense of
privacy and anonymity that is fostered to an extreme in certain subcultures of
the Internet.~\cite[588]{prichard:subcultures} Research reveals that piracy and
piracy-adjacent tools provide the means to distribute this disgusting content
to unimaginable scales. Prichard et al explored this area of research, with
the following conclusions:
\blockcquote[593]{prichard:subcultures}{%
  Based on longitudinal data collected between August and November 2010, this
  study screened for the search terms that still appeared in the isoHunt Top
  300 list in November after being observed during August. In summary, the
  study found that 158/162 search terms related to infringing content, while
  3/162 search terms related to child pornography and 1/162 to bestiality%
}
These numbers may seem small to many. To properly interpret the above numbers,
consider that: 1) they do not represent the quantity of files that are shared
and 2) the researchers focused on isoHunt (which operated on the surface web)
and did not explore other means to find torrent files (i.e., means that utilize
the anonymity of the dark web). The numbers, rather, represent the consistent
interest within certain online subcultures in the immoral content. This
consistency presents a really compelling argument for Christians to question
piracy and the online culture that promotes and uses these methods.

@@

This may be an unsatisfactory and complex answer to a large and complex issue.
Piracy (namely in the form of torrenting) does, however, rely on peers to
seed the content, and if changes can be made in these subcultures of the
internet. Because of the (mostly) decentralized nature of piracy, the best hope
is for the popular sites and individuals to self-regulate the content that is
promoted or accepted. For Christians, one option to keep in mind or consider
is to evangelize or set an example of what good online behavior looks like.
These questions of regulation and changes in the online culture, however,
reside outside the scope of this paper, but they, nevertheless, remain (and
will remain) increasingly relevant.

@@

On the one hand, a Christian use of piracy should be respectful of authority.
We are called to do this regardless of punishment, but as a matter of
conscience (Romans 13:4--5). We are to exercise our freedom respectfully and
not as a cover-up for evil (1 Peter 2:13--7). In other words, we should consider
both the consequences we may incur and the image we portray carefully before
making a conclusion about the practice of piracy. A proper consideration of
piracy should not ignore the serious ramifications and associations that come
with it.

@@

\clearpage
\printbibliography[title=References]
\end{refsection}

\clearpage
\nocite{*}
\printbibliography[title=Bibliography]
\end{document}
